%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Specifications %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article} 
\usepackage[letterpaper,margin=0.6in]{geometry}
\usepackage{multicol}
\usepackage{url}
\usepackage[pdftex]{hyperref}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Name & Contact Info %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
	{\Large \bfseries Jin Che} \\ 
	{\large Curriculum Vitae} \\
\end{center}

% \vspace{0.15in}

{\noindent \bf Contact Information} \\ 
Email: \href{mailto:jin.che@mail.utoronto.ca}{jin.che@mail.utoronto.ca} \\ 
Phone: +1 778 323 9958 \\ 
LinkedIn: \href{https://www.linkedin.com/in/jin-che-6a1277201/}{https://www.linkedin.com/in/jin-che-6a1277201} \\ 
Github: \href{https://github.com/bcTornado608}{https://github.com/bcTornado608} \\

\vspace{0.15in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\noindent \bfseries EDUCATION}
\vspace{0.05in}
\hline

\vspace{0.1in}

\noindent
{\sl \bfseries Ph.D. in Electrical Engineering} \hfill 2025 - present \\
\noindent University of Toronto, Toronto, ON, Canada \\
\noindent Supervisor: Prof. Antonio Liscidini \\

\noindent
{\sl \bfseries Bachelor of Applied Science in Electrical Engineering} \hfill 2020 - 2025 \\
\noindent University of Toronto, Toronto, ON, Canada \\
\noindent cGPA: 3.80/4.00 \\

\vspace{0.15in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RESEARCH INTEREST %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\noindent \bfseries RESEARCH INTEREST}
\vspace{0.05in}
\hline

\vspace{0.1in}
\noindent
Integrated Circuits; RF Circuit Design; Biomedical Electronics; Sensing   \\

\vspace{0.15in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RESEARCH INTERNSHIPS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\noindent \bfseries RESEARCH INTERNSHIPS}
\vspace{0.05in}
\hline

\vspace{0.1in}

\noindent
{\sl \bfseries Research Assistant} \hfill 2024/05 - 2025/05 \\
\noindent Intelligent Sensory Microsystems Laboratory, University of Toronto \hfill Ontario, Canada \\
Faculty Mentor: Prof. Roman Genov

\begin{itemize} \itemsep -2pt
	\item Focused on designing, simulating, and testing advanced PCB systems, including wireless energy harvesting and neural stimulation.
	\item Developed control logic for a SAR ADC on FPGA, and performed spike sorting with basic machine learning algorithms.
    \item Contributed to multiple research projects, submitted to the IEEE ISSCC, involving ADC designs and neural stimulation systems.
\end{itemize}

\vspace{0.15in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROFESSIONAL EXPERIENCE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\noindent \bfseries PROFESSIONAL EXPERIENCE}
\vspace{0.05in}
\hline

\vspace{0.1in}

\noindent
{\sl \bfseries ASIC Design Engineer, Intern} \hfill 2023/05 - 2024/05 \\
\noindent Advanced Micro Devices, Inc. \hfill Ontario, Canada \\
\noindent Supervisor: Zehra Allabachayo

\begin{itemize} \itemsep -2pt
	\item Upgraded and maintained the debug bus and performance counter design in the PCIe transaction layer sub-IP.
	\item Managed clock domain crossing and lint violations to ensure smooth design operations.
    \item Initialized new project variants, debugging build failures, and making code and parameter adjustments.
    \item Optimized design infrastructure by updating components and improving power efficiency using power clamps.
\end{itemize}

\vspace{0.15in}

%%%%%%%%%%%%%%%%%%%%%%%%%%% PROJECTS %%%%%%%%%%%%%%%%%%%%%%%%%%%

{\noindent \bfseries PROJECTS}
\vspace{0.05in}
\hline

\vspace{0.1in}

\noindent
{\sl \bfseries Brainzoom} \hfill Ontario, Canada \\
\noindent Intelligent Sensory Microsystems Laboratory

\begin{itemize} \itemsep -2pt
	\item Designed COB (chip-on-board) for a next-generation ADC design specialized for brain activity recording.
    \item Led the assembly and testing of the boards, ensuring thorough validation of system functionality.
\end{itemize}

\vspace{0.05in}

\noindent
{\sl \bfseries Netron} \hfill Ontario, Canada \\
\noindent Intelligent Sensory Microsystems Laboratory

\begin{itemize} \itemsep -2pt
	\item Designed and tested control logic for a Successive Approximation Register (SAR) ADC on an FPGA board.
    \item Performed spike sorting using k-means clustering on neural data from both in vivo and in vitro experiments, recorded with our custom-designed ADC.
\end{itemize}

\vspace{0.05in}

\noindent
{\sl \bfseries PNS with Machine Learning Mediated Dynamic Power Supply} \hfill Ontario, Canada \\
\noindent Intelligent Sensory Microsystems Laboratory

\begin{itemize} \itemsep -2pt
	\item Led the design and layout of the project from scratch, testing the printed circuit board and running experiments on neural tissue.
    \item Programmed a microcontroller to learn voltage patterns across neural tissues using machine learning techniques.
\end{itemize}

\vspace{0.05in}

% \noindent
% {\sl \bfseries Small Robotic Vehicle with Auto Routing} \hfill Ontario, Canada \\
% \noindent University of Toronto Robotics Association

% \begin{itemize} \itemsep -2pt
% 	\item Led a team of four in a hackathon to design a robotic vehicle with obstacle avoidance and autonomous driving capabilities, securing first place.
%     \item Developed sensor positioning and Bluetooth wireless control, integrating infrared and ultrasonic sensors for navigation.
% \end{itemize}

\vspace{0.15in}

%%%%%%%%%%%%%%%%%%%%%%%%%%% PUBLICATIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%

{\noindent \bfseries PUBLICATIONS}
\vspace{0.05in}
\hline

\vspace{0.1in}

\noindent
{\sl \bfseries Conference Paper (Peer Reviewed):}

\noindent
J. Xu, M. Kanchwala, M. Abdolrazzaghi, H. Cai, Y. Huang, J. Ma, C. Lim, L. Xu, S. Gong, W. Deng, Q. Deng, \textbf{J. Che}, S. Nag, J. Olorocisimo, R. Singh, Y. Wang, J. Sales Filho, M. Mohaved, H. Moradi, G. Eleftheriades, T. Valiante, and R. Genov, \textbf{"Event-Based Spatially Zooming Neural Interface IC with 10nW/Input Reconfigurable-Inverter Fabric and Input-Adaptive Quantization."} in Proceedings of IEEE International Solid‑State Circuits Conference (ISSCC 2025), Session 15.5, pp. 274–276, San Francisco, CA, USA, Feb 18 2025. \\

\noindent
{\sl \bfseries Journal Article (Peer‑Reviewed):}

\noindent
S. Nag, A. Remadevi, \textbf{J. Che}, M. Prytula, Hanzhang Xing, Hanrui Xing, X. Xiao, A. Constas‑Malvanets, H. Zhang, Y. Sun, J. Olorocisimo, J. Zariffa, and R. Genov, \textbf{“Energy‑Efficient Adaptive Neural Stimulator with Waveform Prediction by Sub‑Threshold Interrogation of the Electrode‑Tissue Interface.”} in IEEE Transactions on Biomedical Circuits and Systems, vol. PP, no. 99 (early access), May 2025. DOI: 10.1109/TBCAS.2025.3570264. \\

\vspace{0.15in}

%%%%%%%%%%%%%%%%%%%%%%%%%%% SCHOLARSHIPS & AWARDS %%%%%%%%%%%%%%%%%%%%%%%%%%%

{\noindent \bfseries SCHOLARSHIPS \& AWARDS}
\vspace{0.05in}
\hline

\vspace{0.1in}

\noindent
{NSERC USRA Summer Award (\$7,500)} \hfill 2024/04
\vspace{0.05in}

\noindent
{Edward S Rogers Sr. Admission Scholarship (\$1,000)} \hfill 2020/10 
\vspace{0.05in}

\noindent
{Faculty Of Applied Science And Engineering Admission Scholarship (\$222)} \hfill 2020/10 
\vspace{0.05in}

\noindent
{Wallberg Admission Scholarships (\$5,000)} \hfill 2020/10 
\vspace{0.15in}
\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%% Skills & Tools %%%%%%%%%%%%%%%%%%%%%%%%%%%
{\noindent \bfseries SKILLS \& TOOLS}
\vspace{0.05in}
\hline
\vspace{0.1in}
\noindent
{\sl \bfseries Tools:} Cadence Virtuoso, Altium Designer, Intel Quartus Prime, AMD Vivado, Verdi, Spyglass Lint, Modelsim\\
{\sl \bfseries Skills:} IC Design and Layout, PCB Design, Signal Processing, Verilog, C, C++, Perl, Python, Java, ARM Assembly
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
